---
title: "Meta Smart Glasses Review Intelligence"
author: "Girika"
format:
  html:
    toc: true
    toc-depth: 3
    number-sections: true
    theme: cosmo
execute:
  echo: true
  warning: false
  message: false
---

## Meta Smart Glasses

***Meta's Display Glasses, Smart AI Glasses for Men and Women***

```{r}
#| label: setup
#| include: false

pkgs <- c(
"tidyverse", "janitor", "lubridate", "skimr",
"knitr", "kableExtra", "scales", "stringr", "forcats"
)

to_install <- pkgs[!pkgs %in% installed.packages()[, "Package"]]
if (length(to_install) > 0) install.packages(to_install)

invisible(lapply(pkgs, library, character.only = TRUE))

theme_set(theme_minimal(base_size = 12))
options(scipen = 999)

```

### MAIN AIM

The aim of this project is to convert raw customer reviews into actionable product and marketing insights for Meta Smart Glasses. Specifically, this analysis seeks to:

- Describe overall customer satisfaction patterns using star ratings.
- Compare review behaviour across verified vs non-verified purchases (where available).
- Examine geographic and time patterns in review volume and ratings.
- Investigate factors associated with “helpful” reviews (e.g., review length, rating extremity).

The output of this phase is a clean, reproducible exploratory analysis, supported by professional tables and visualisations.


```{r}
# Load required libraries
library(tidyverse)
library(janitor)
library(dplyr)
```

```{r}
# Load the dataset
reviews_raw <- read_csv("data/Meta-Glasses-Reviews.csv")

# Clean column names
reviews <- reviews_raw %>%
  clean_names()

```
```{r}

reviews_clean <- reviews %>%
  select(
    -review_id,
    -name,
    -profile,
    -review_link,
    -review_image
  )
write_csv(
  reviews_clean,
  "data/meta_reviews_selected_columns.csv"
)

```

